### 2025-05-05 Chapters/paper2.tex
changes of paper 2

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{\img/paper_2/Comparision Plot.png}
	\caption{Accuracy Comparison Plot}
	\label{fig:accuracy_comparison}
\end{figure}

\subsection{Neural Network Comparison}
The performance of the Neural Network model is compared in the plot below, showing its accuracy.

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{\img/paper_2/neural network comparison .png}
	\caption{Neural Network Comparison}
	\label{fig:nn_comparison}
\end{figure}

\subsection{Bi-LSTM Performance}
The Bi-LSTM model's accuracy is evaluated and compared with other models.

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{\img/paper_2/BILSTM Accuaracy Plot.png}
	\caption{Bi-LSTM Accuracy Plot}
	\label{fig:bilstm_accuracy}
\end{figure}

\subsection{LSTM Performance}
The following figure shows the accuracy of the LSTM model, highlighting its effectiveness in comparison to other models.

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{\img/paper_2/lstm accuracy and loss plot.png}
	\caption{LSTM Accuracy and Loss Plot}
	\label{fig:lstm_accuracy}
\end{figure}

\subsection{RNN Performance}
Lastly, the performance of the RNN model is shown below.

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{\img/paper_2/Rnn Accuracy Plot.png}
	\caption{RNN Accuracy Plot}
	\label{fig:rnn_accuracy}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.70\textwidth]{img/paper_2/sleep event.PNG}
	\caption{Event Mapping Plot}
	\label{fig:lstm_accuracy}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_2/Comparision Plot.png}
		\caption{Accuracy Comparison Across All Models}
		\label{fig:accuracy_comparison}
	\end{minipage}
	\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_2/BILSTM.png}
		\caption{Bi-LSTM Model Performance}
		\label{fig:bilstm_performance}
	\end{minipage}

	\vspace{0.5cm}

	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_2/LSTM.png}
		\caption{LSTM Model Performance}
		\label{fig:lstm_performance}
	\end{minipage}
	\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_2/RNN.png}
		\caption{RNN Model Performance}
		\label{fig:rnn_performance}
	\end{minipage}
\end{figure}
